Numerical simulation of the shallow water circular hydraulic jump

### 2020-09-16 numerics_paper/numerical_chj.tex
More PyClaw results in paper.

>>>>

The results above are computed with schemes that include second-order
correction terms.  In Figure \ref{fig:first-order} we compare the corresponding
first-order schemes.  Even by increasing the value of $\epsilon$ to $0.1$,
the carbuncles are not suppressed by the HLLEMCC solver.  Indeed, the Roe
and HLLEMCC solutions look very similar.

\begin{figure}
  \begin{centering}
    \subfloat[Roe Riemann solver, 1st order, t=20]{
      \includegraphics[width=0.45\textwidth]{figures/_1_roe_1000_t20.eps} 
    }
    \subfloat[HLLEMCC Riemann solver, $\epsilon=0.1$, 1st order, t=20]{
      \includegraphics[width=0.45\textwidth]{figures/_1_hllemcc_1000_eps01_t20.eps}
    }
  \end{centering}
  \caption{
    PyClaw solutions using a 1st-order discretization
    with different Riemann solvers.\label{fig:hllemcc}}
\end{figure}
